
---
title: "Test Time Functions"
output: html_notebook
---

```{r}
library(here)
library(arrow)
source(here("src", "R", "scripts.R"))
options(digits=10)
```

# Calculate the mean and apparent sidereal time at Greenwich on 1987 April 10
# at 0 hours universal time
```{r}
year <- 1987
month <- 4
day <- 10
jd <- julianDayNumber(year, month, day)
dt <- deltaT(year, month)
st <- gst(jd, dt)
print("Greenwich Mean Sidereal Time (GMST) = ")
gmst <- hourToHMS(st[[1]][1]*RAD2HR)
hmsString(gmst)
print("Greenwich Apparent Sidereal Time (GAST) = ")
gast <- hourToHMS(st[[2]][1]*RAD2HR)
hmsString(gast)
```
# Find the mean and apparent sidereal time at Greenwich on 1987 April 10 at
# 19 hours 21 minutes and 0 seconds universal time
```{r}
hms <- c(19, 21, 0)
hour <- hmsToHour(hms)
jd <- julianDayNumber(1987, 4, (10+hour/24))
dt <- deltaT(year, month)
st <- gst(jd, dt)
print("Greenwich Mean Sidereal Time (GMST) = ")
gmst <- hourToHMS(st[[1]][1]*RAD2HR)
hmsString(gmst)
print("Greenwich Apparent Sidereal Time (GAST) = ")
gast <- hourToHMS(st[[2]][1]*RAD2HR)
hmsString(gast)
```

# Calculate the hour angle of the Sun for a single day using the right ascension
```{r}
# Right Ascension in hours of the Sun on January 23, 2023
ra <-hmsToHour(c(20, 19, 54)) * HR2RAD
obsLong <- -96.5391 * DEG2RAD
year <- 2023
month <- 1
day <- 22.5
jd <- julianDayNumber(year, month, day+4/24)
dt <- deltaT(year, month)
st <- gst(jd, dt)
lha <- st[[1]][1] - obsLong - ra
lha <- lha*RAD2HR
print(lha)
```


# Test local civil time to universal time function, no daylight savings time
# Eastern standard time zone
```{r}
hr <- localCivilTimeToUniversalTime(18, FALSE, -5)
print("Local Civil Time in hours")
hr
```


# Test local civil time to universal time function, with daylight savings time
# Eastern standard time zone
```{r}
hr <- localCivilTimeToUniversalTime(18, TRUE, -5)
print("Local Civil Time in hours")
hr
```


# Test universal time to local civil function, no daylight savings time
# Eastern standard time zone
```{r}
hr <- universalTimeToLocalCivilTime(23.5, FALSE, -5)
print("Universal Time in hours")
hr
```


# Test universal time to local civil function, with daylight savings time
# Eastern standard time zone
```{r}
hr <- universalTimeToLocalCivilTime(23.5, TRUE, -5)
print("Local Civil Time in hours")
hr
```


```{r}
hr <- localCivilTimeToUniversalTime(20, FALSE, -5)
print("Local Civil Time in hours")
hr
```
