---
title: "Test JPL DE441 Data"
output: html_notebook
---

```{r}
library(here)
library(arrow)
source(here("src", "R", "scripts.R"))
options(digits = 12)
```

# Test the JPL DE441 data extracted from the ASCII files

# Position and velocity vectors of Mercury on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionMercurySSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of Venus on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionVenusSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of the Earth-Moon Barycenter on December 15, 2019.
# The reference frame for the position and velocity vectors is equatorial. Convert
# the vectors to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionEMBSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of Earth on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionEarthSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of Mars on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionMarsSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```


# Position and velocity vectors of Jupiter on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionJupiterSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of Saturn on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionSaturnSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of Uranus on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionUranusSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of Neptune on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionNeptuneSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of Pluto on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionPlutoSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of Moon on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionMoonGEO(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Position and velocity vectors of Sun on December 15, 2019. The reference 
# frame for the position and velocity vectors is equatorial. Convert the vectors
# to right ascension and declination.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
pos <- positionSunSSB(jd)
pos["Position Vector"]
pos["Velocity Vector"]
raDec <- rectToPolar(pos["Position Vector"])
print("Right Ascension")
hmsString(hourToHMS(raDec[3]))
print("Declination")
dmsString(degToDMS(raDec[2]))
```

# Nutation angles (nutation in longitude and nutation in obliquity)
# on December 15, 2019.
```{r}
year <- 2019
month <- 12
day <- 15
jd <- julianDayNumber(year, month, day)
nutAngles <- nutationAngles(jd)
print("Nutation in Longitude")
nutAngles[1]
dmsString(degToDMS(nutAngles[[1]][1]))
print("Nutation in Obliquity")
nutAngles[2]
dmsString(degToDMS(nutAngles[[2]][1]))
```

