---
title: "Test Coordinate Transforms"
output: html_notebook
---


```{r}
library(here)
library(arrow)
source(here("src", "R", "scripts.R"))
```


# Convert horizon coordinates to equatorial coordinates
# Altitude, azimuth, and latitude all in degrees
```{r}
altitude <- 40
azimuth <- 115
latitude <- 38
coord <- horizonToEquatorial(azimuth, altitude, latitude)
print("Hour Angle")
hmsString(hourToHMS(coord[[1]][[1]]))
print("Declination")
dmsString(degToDMS(coord[[2]][[1]]))
```


# Convert equatorial coordinates to horizon coordinates
# Declination in degrees, arcminutes, and arcseconds
# Hour Angle in hours, minutes, and seconds
# Latitude in degrees
```{r}
dec <- dmsToDeg(c(0,-30,30))
hrAng <- hmsToHour(c(16, 29, 45))
latitude <- 25
coord <- equatorialToHorizon(hrAng, dec, latitude)
print("Azimuth")
dmsString(degToDMS(coord[[1]][[1]]))
print("Altitude")
dmsString(degToDMS(coord[[2]][[1]]))
```


# Convert equatorial coordinates to ecliptic coordinates
# Right ascension in hours, minutes, and seconds
# Declination in degrees, arcminutes, and arcseconds
# Obliquity - Standard Epoch J2000
```{r}
ra <- hmsToHour(c(12, 18, 47.5))
dec <- dmsToDeg(c(0, -43, 35.5))
jd <- julianDayNumber(2000, 1, 1.5)
nutAng <-  nutationAngles(jd)
obliqJ2000 <- obliquity(jd, nutAng)
obMean <- obliqJ2000[[1]][[1]] * RAD2DEG
eclipt <- equatorialToEcliptic(ra, dec, obMean)
print("Ecliptic Longitude - Lambda")
dmsString(degToDMS(eclipt[[2]][[1]]))
print("Ecliptic Latitude - Beta")
dmsString(degToDMS(eclipt[[1]][[1]]))
```

# Convert ecliptic coordinates to equatorial coordinates
# Ecliptic latitude - beta in degrees, arcminutes, and arcseconds
# Ecliptic longitude in degrees, arcminutes, and arcseconds
# Obliquity - Standard Epoch J2000
```{r}
beta <- dmsToDeg(c(1, 12, 0))
lambda <- dmsToDeg(c(184, 36, 0))
jd <- julianDayNumber(2000, 1, 1.5)
nutAng <-  nutationAngles(jd)
obliqJ2000 <- obliquity(jd, nutAng)
obMean <- obliqJ2000[[1]][[1]] * RAD2DEG
equat <- eclipticToEquatorial(beta, lambda, obMean)
print("Right Ascension")
dmsString(degToDMS(equat[[1]][[1]]))
print("Declination")
dmsString(degToDMS(equat[[2]][[1]]))
```
